Manuscript simulations

### 2023-02-24 Manuscript simulations.Rmd
progress on simulations - rewrote coral model in nimble

# packages
packs <- c("dplyr", "nimble", "htmltools", "ggplot2", "sf", "Rcpp", "RcppArmadillo", "inline", "mvtnorm", "readr", "parallel", "xtable", "rstan", "coda", "vegan", "tidyr", "stringr", "tidyverse", "plotly", "CommEcol")
sapply(packs, require, character.only = T)
rm(packs)

# convenience
`%notin%` <- Negate("%in%")
options(mc.cores = parallel::detectCores())
```

```{r}
nimble_summary <- function(fit, warmup = nrow(fit[[1]])/2, thin = 1){
  # convert to coda for normal summary
  fit_warmup <- lapply(fit, function(x) x[(warmup+1):nrow(x),])
  coda_samples <- as.mcmc.list(lapply(fit_warmup, function(x) as.mcmc(
    x, start = warmup+1, end = nrow(fit), thin = thin
  )))

  sum <- summary(coda_samples)
  params <- dimnames(sum$statistics)[[1]]
  tmp_sum <- cbind(sum$statistics, sum$quantiles)

  # get r hat / n_eff
  mat <- matrix(NA, nrow = nrow(tmp_sum), ncol = 3)
  colnames(mat) <- c("Rhat", "ess_bulk", "ess_tail")
  for(i in 1:nrow(tmp_sum)){
    tmp <- sapply(fit, function(x) x[,i])
    mat[i,] <- c(Rhat(tmp), ess_bulk(tmp), ess_tail(tmp))
  }

  # out 
  out <- cbind(tmp_sum, mat)
  return(out)
}

fit_model <- function(seed = 1, code, data, constants, inits, niter, nchains, thin = 1){
  library(nimble)

  # R model
  model <- nimbleModel(code, constants, data)

  # C model
  model_c <- compileNimble(model)

  # R mcmc
  model_conf <- configureMCMC(model)
  model_conf$addMonitors(c("clus_id", "z"))

  # R mcmc
  mcmc <- buildMCMC(model_conf)

  # C mcmc
  mcmc_c <- compileNimble(mcmc, project = model_c)

  # run model
  out <- runMCMC(
    mcmc_c, 
    niter = niter, 
    nchains = nchains, 
    thin = thin, 
    init = inits,
    setSeed = seed
  )

  # out
  return(out)
}

ord_ls <- function(mcmc, d = 2, seed = NULL, force_K = NULL){
  # optional seed
  if(!is.null(seed)) set.seed(seed)

  # housekeeping
  mu <- lapply(mcmc, function(x) x[,which(grepl("mu", colnames(x)))])
  clus_id <- lapply(mcmc, function(x) x[,which(grepl("clus_id", colnames(x)))])
  other_ndx <- c(1:length(colnames(mcmc[[1]])))[-c(
    sort(c(
      which(grepl("clus_id", colnames(mcmc[[1]]))), 
      which(grepl("mu", colnames(mcmc[[1]])))
    ))
  )]
  other <- lapply(mcmc, function(x) x[,other_ndx])

  mu_mcmc <- do.call("rbind", mu)
  clus_mcmc <- do.call("rbind", clus_id)
  other_mcmc <- do.call("rbind", other)

  # helper function
  getmode <- function(v) {
    uniqv <- unique(v)
    uniqv[which.max(tabulate(match(v, uniqv)))]
  }

  # step 1 - determine number of non-empty cluster for each iteration
  n_clus_mcmc <- apply(clus_mcmc, 1, function(x) length(unique(x)))

  # step 2 - estimate the mode
  if(is.null(force_K)){
    n_clus_mode <- getmode(n_clus_mcmc)
  } else{
    n_clus_mode <- force_K
  }

  # step 3 - filter to iterations with n_clus_mcmc = n_clus_mode
  ## filter first
  which_equal_mode_index <- which(n_clus_mcmc == n_clus_mode)
  mu_mcmc_filtered <- mu_mcmc[which_equal_mode_index, ]
  clus_mcmc_filtered <- clus_mcmc[which_equal_mode_index, ]
  other_mcmc_filtered <- other_mcmc[which_equal_mode_index, ]

  ## remove empty clusters - loop
  mu_reduced <- matrix(NA, nrow = nrow(mu_mcmc_filtered), ncol = n_clus_mode * d)
  clus_reduced <- array(NA, dim = dim(clus_mcmc_filtered))
  for(i in 1:length(which_equal_mode_index)){
    clus_id_i <- sort(unique(clus_mcmc_filtered[i, ]))
    col_ndx <- which(
      stringr::str_sub(
        colnames(mu_mcmc_filtered), 
        start = stringr::str_locate(colnames(mu_mcmc_filtered), pattern = "\\[")[,1] + 1,
        end = stringr::str_locate(colnames(mu_mcmc_filtered), pattern = "\\,")[,1] - 1
      ) %in% clus_id_i
    )

    mu_reduced[i, ] <- mu_mcmc_filtered[i,col_ndx]
    colnames(mu_reduced) <- paste0("mu[", rep(1:n_clus_mode, d), ", ", rep(1:d, each = n_clus_mode), "]")
    clus_reduced[i, ] <- as.numeric(factor(clus_mcmc_filtered[i,]))
    colnames(clus_reduced) <- colnames(clus_mcmc_filtered)
  }

  # step 4 - create data matrix, cluster with k-means
  data_matrix <- matrix(
    c(mu_reduced), 
    nrow = nrow(mu_reduced) * n_clus_mode,
    ncol = d
  )
  k_means <- kmeans(data_matrix, centers = n_clus_mode)
  rho <- matrix(k_means$cluster, nrow = nrow(mu_reduced), ncol = n_clus_mode)

  # step 5 - check whether rho_i is a permutation of 1:n_clus_mode
  keep_ndx <- which(apply(rho, 1, function(x) all(sort(x) == 1:n_clus_mode)))
  mu_reduced <- mu_reduced[keep_ndx,]
  clus_reduced <- clus_reduced[keep_ndx,]
  other_reduced <- other_mcmc_filtered[keep_ndx, ]
  rho <- rho[keep_ndx,] %>% as.matrix(., ncol = n_clus_mode)

  # step 6 - relabel according to rho
  ## relabel mus first - works, but slow
  mu_relabeled <- array(NA, dim = dim(mu_reduced))
  colnames(mu_relabeled) <- colnames(mu_reduced)
  for(i in 1:nrow(mu_relabeled)){
    for(j in 1:ncol(mu_relabeled)){
      # get group id
      group_id <- stringr::str_sub(
        colnames(mu_reduced)[j], 
        start = stringr::str_locate(colnames(mu_reduced)[j], pattern = "\\[")[,1] + 1,
        end = stringr::str_locate(colnames(mu_reduced)[j], pattern = "\\,")[,1] - 1
      ) %>% as.numeric()

      dim_id <- stringr::str_sub(
        colnames(mu_reduced)[j], 
        start = stringr::str_locate(colnames(mu_reduced)[j], pattern = "\\,")[,1] + 1,
        end = stringr::str_locate(colnames(mu_reduced)[j], pattern = "\\]")[,1] - 1
      ) %>% as.numeric()

      # replace with proper value according to rho
      rho_i <- rho[i, ]
      mu_relabeled[i,j] <- mu_reduced[i, which(
        colnames(mu_reduced) == paste0("mu[", which(rho_i == group_id), ", ", dim_id, "]")
      )]
    }
  }

  ## relabel clus_id's
  clus_relabeled <- array(NA, dim = dim(clus_reduced))
  colnames(clus_relabeled) <- colnames(clus_reduced)
  for(i in 1:nrow(clus_relabeled)){
    rho_i <- rho[i,]
    clus_id_i <- clus_reduced[i,]
    clus_relabeled[i,] <- sapply(clus_id_i, function(x) rho_i[x])
  }

  out <- list(
    mu = mu_relabeled, 
    clus_id = clus_relabeled, 
    other = other_reduced,
    which_iter = which_equal_mode_index[keep_ndx]
  )

  return(out)
}

waic_dpord <- function(Y, mcmc, frame_ind, hier = F){
  if(hier){
    # get params 
    mu <- samples_relabeled$mu
    clus_id <- samples_relabeled$clus_id
    other <- samples_relabeled$other
    alpha <- other[,grepl("alpha", colnames(other))]
    beta <- other[,grepl("beta", colnames(other))]
    gamma <- other[,grepl("gamma[[]", colnames(other))]
    z <- other[,grepl("z", colnames(other))]
    theta <- other[,grepl("theta", colnames(other))]

    # get dimension
    d <- sapply(colnames(mu), function(x){
      str_sub(x, start = nchar(x)-1, end = nchar(x)-1)
    }) %>% as.numeric %>% max

    # compute lppd
    ## lik = alpha[i] + beta[j] + z[i] theta[j] + gamma[i]
    log_py <- matrix(NA, nrow = nrow(z), ncol = length(c(Y)))
    message("Calculating log likelihood")
    pb <- txtProgressBar(min = 0, max = nrow(log_py), style = 3, char = "=")
    for(iter in 1:nrow(log_py)){
      alpha_vec_s <- alpha[iter,]
      beta_vec_s <- beta[iter,]
      z_matrix_s <- matrix(z[iter,], ncol = d)
      z_matrix_s <- z_matrix_s[rep(1:nrow(z_matrix_s), table(frame_ind)),]
      theta_matrix_s <- matrix(theta[iter,], ncol = d)
      gamma_s <- gamma[iter, ]

      linpred <- rep(rep(alpha_vec_s, table(frame_ind)), ncol(Y)) +
        rep(beta_vec_s, each = nrow(Y)) +
        c(z_matrix_s %*% t(theta_matrix_s)) +
        rep(gamma_s, ncol(Y))
      pi <- unname(exp(linpred) / (1 + exp(linpred)))

      # fix numerical issues
      pi[which(pi > 0.99999)] <- 0.99999
      pi[which(pi < 0.00001)] <- 0.00001

      log_py[iter,] <- c(Y) * log(pi) + (1 - c(Y)) * log(1 - pi)
      setTxtProgressBar(pb, iter)
    }
    close(pb)

    # compute lppd
    message("Computing lppd")
    lppd <- sum(log(colMeans(exp(log_py))))

    # compute penalty
    message("Computing penalty")
    pwaic2 <- sum(apply(log_py, 2, function(x) var(x)))

    # compute waic
    waic <- -2*(lppd - pwaic2)
    out <- waic
  } else{
    # get params 
    mu <- samples_relabeled$mu
    clus_id <- samples_relabeled$clus_id
    other <- samples_relabeled$other
    alpha <- other[,grepl("alpha", colnames(other))]
    beta <- other[,grepl("beta", colnames(other))]
    z <- other[,grepl("z", colnames(other))]
    theta <- other[,grepl("theta", colnames(other))]

    # get dimension
    d <- sapply(colnames(mu), function(x){
      str_sub(x, start = nchar(x)-1, end = nchar(x)-1)
    }) %>% as.numeric %>% max

    # compute lppd
    ## lik = alpha[i] + beta[j] + z[i] theta[j] + gamma[i]
    log_py <- matrix(NA, nrow = nrow(z), ncol = length(c(Y)))
    message("Calculating log likelihood")
    pb <- txtProgressBar(min = 0, max = nrow(log_py), style = 3, char = "=")
    for(iter in 1:nrow(log_py)){
      alpha_vec_s <- alpha[iter,]
      beta_vec_s <- beta[iter,]
      z_matrix_s <- matrix(z[iter,], ncol = d)
      theta_matrix_s <- matrix(theta[iter,], ncol = d)

      linpred <- rep(alpha_vec_s, ncol(Y)) +
        rep(beta_vec_s, each = nrow(Y)) +
        c(z_matrix_s %*% t(theta_matrix_s)) 
      pi <- unname(exp(linpred) / (1 + exp(linpred)))

      # fix numerical issues
      pi[which(pi > 0.99999)] <- 0.99999
      pi[which(pi < 0.00001)] <- 0.00001

      log_py[iter,] <- c(Y) * log(pi) + (1 - c(Y)) * log(1 - pi)
      setTxtProgressBar(pb, iter)
    }
    close(pb)

    # compute lppd
    message("Computing lppd")
    lppd <- sum(log(colMeans(exp(log_py))))

    # compute penalty
    message("Computing penalty")
    pwaic2 <- sum(apply(log_py, 2, function(x) var(x)))

    # compute waic
    waic <- -2*(lppd - pwaic2)
    out <- waic
  }

  return(out)
}

getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}
```

@@

```{r}
set.seed(02212023)
coords <- rbind(
  mvtnorm::rmvnorm(15, c(30, 60), 30*diag(2)),
  mvtnorm::rmvnorm(15, c(60, 40), 30*diag(2)),
  mvtnorm::rmvnorm(15, c(80, 60), 30*diag(2))
)
plot(coords, col = rep(1:3, each = 15), main = "True latent coordinates")
mat <- compas(
  S = 30, 
  dims = 2,
  am = c(5, 5),
  beta.R = c(1, 1), 
  coords = coords, 
  n.quanti = 1,
  n.quali = 0.05, 
  add1 = 0.05
)
# mat[mat > 1] <- 1
mat <- mat[which(rowSums(mat) != 0),]
```

@@

```{r}
nmds <- vegan::metaMDS(
  mat,
  distance = "bray", 
  k = 3
)
plot(nmds$points)
```

@@

```{r}
library(gmp)
# probability mass function from Antoniak (1974)
antoniak <- function(k, alpha, n){
  alpha <- gmp::as.bigq(as.character(MASS::fractions(alpha)))

@@

```{r}
# model based 
code <- nimbleCode({
  # priors
  phi ~ dunif(0, 10)
  ## site effects
  for(site in 1:nsites){
    alpha[site] ~ dnorm(0, 1)
  }

@@

  ## z priors
  ### Dirichlet process mixture parameters
  clus_id[1:nsites] ~ dCRP(dp_con, size = nsites)
  dp_con ~ dgamma(1, 1)

@@

this_cluster <- makeCluster(3)
fit <- parLapply(
  cl = this_cluster,
  X = 1001:1003,
  fun = fit_model,
  code = code,
  data = list(
    Y = mat,
    S = diag(2),
    mu0 = rep(0, 2),
    Lambda0 = diag(2)
  ),
  constants = list(
    nsites = nrow(mat),
    nspecies = ncol(mat),
    d = 2,
    max_clus = 40
  ),
  inits = init_func,
  niter = 10000,
  nchains = 1,
  thin = 1
)
stopCluster(this_cluster)
```

```{r}
fit_ <- fit
fit <- lapply(fit, function(x) x[(nrow(x)/2 + 1):nrow(x), ])
samples_relabeled <- ord_ls(mcmc = fit[c(1:3)], d = 2, seed = 02212023)

z_mcmc <- samples_relabeled$other[,which(grepl("z", colnames(samples_relabeled$other)))]
z_tbl <- left_join(
  tibble(
    trace = c(z_mcmc),
    param = rep(colnames(z_mcmc), each = nrow(z_mcmc)),
    iter = rep(1:nrow(z_mcmc), length(colnames(z_mcmc))),
    obs_id = stringr::str_sub(
      param, 
      start = stringr::str_locate(param, pattern = "\\[")[,1] + 1,
      end = stringr::str_locate(param, pattern = "\\,")[,1] - 1
    ) %>% as.numeric(),
    dim = stringr::str_sub(
      param, 
      start = stringr::str_locate(param, pattern = "\\,")[,1] + 1,
      end = stringr::str_locate(param, pattern = "\\]")[,1] - 1
    ) %>% as.numeric()
  ),
  tibble(
    clus_id = c(samples_relabeled$clus_id),
    iter = rep(1:nrow(samples_relabeled$clus_id), length(colnames(samples_relabeled$clus_id))),
    obs_id = rep(1:ncol(samples_relabeled$clus_id), each = nrow(samples_relabeled$clus_id))
  ),
  by = c("iter", "obs_id")
)

@@

How complex?

>>>>

# packages
packs <- c("dplyr", "nimble", "htmltools", "ggplot2", "sf", "Rcpp", "RcppArmadillo", "inline", "mvtnorm", "readr", "parallel", "xtable", "rstan", "coda", "vegan", "tidyr", "stringr", "tidyverse", "plotly", "CommEcol", "cluster", "rstan")
sapply(packs, require, character.only = T)
rm(packs)

# convenience
`%notin%` <- Negate("%in%")
options(mc.cores = parallel::detectCores())
source("simulations/helpers.R")
```

```{r}

```

@@

```{r, eval = F}
set.seed(02222023)
coords <- rbind(
  mvtnorm::rmvnorm(15, c(30, 60), 30*diag(2)),
  mvtnorm::rmvnorm(15, c(60, 40), 30*diag(2)),
  mvtnorm::rmvnorm(15, c(80, 60), 30*diag(2))
)
plot(coords, type = "n", main = "True latent coordinates")
text(coords, labels = 1:45, col = rep(1:3, each = 15))
mat <- compas(
  S = 30, 
  dims = 2,
  am = c(5, 5),
  beta.R = c(1, 1), 
  coords = coords, 
  n.quanti = 1,
  n.quali = 0.05, 
  add1 = 0.05
)
# mat[mat > 1] <- 1
mat <- mat[which(rowSums(mat) != 0),]
```

@@

```{r, eval = F}
nmds <- vegan::metaMDS(
  mat,
  distance = "bray", 
  k = 3
)
plot(nmds$points)
```

@@

```{r, eval = F}
library(gmp)
# probability mass function from Antoniak (1974)
antoniak <- function(k, alpha, n){
  alpha <- gmp::as.bigq(as.character(MASS::fractions(alpha)))

@@

```{r, eval = F}
# model based 
code <- nimbleCode({
  # priors
  phi ~ dunif(0, 10)
  ## site effects
  for(site in 1:nsites){
    alpha[site] ~ dnorm(0, 1)
  }

@@

  ## z priors
  ### Dirichlet process mixture parameters
  clus_id[1:nsites] ~ dCRP(dp_con, size = nsites)
  dp_con ~ dgamma(1, 2)

@@

this_cluster <- makeCluster(3)
fit <- parLapply(
  cl = this_cluster,
  X = 1001:1003,
  fun = fit_model,
  code = code,
  data = list(
    Y = mat,
    S = diag(2),
    mu0 = rep(0, 2),
    Lambda0 = diag(2),
    one = rep(1, 2)
  ),
  constants = list(
    nsites = nrow(mat),
    nspecies = ncol(mat),
    d = 2,
    max_clus = 40
  ),
  inits = init_func,
  niter = 75000,
  burnin = 25000,
  nchains = 1,
  thin = 5
)
stopCluster(this_cluster)
```

```{r, eval = F}
source("coral.R")
coral.fit <- fit.coral(y = mat, family = "negative.binomial", num.lv = 2, num.clus = 3, site.eff = TRUE, save.model = F)

plot(coral.fit$lv.mean, type = "n")
text(coral.fit$lv.mean, labels = 1:45, col = coral.fit$clus.modal)
```

```{r, eval = F}
fit_ <- fit
# fit <- lapply(fit, function(x) x[(nrow(x)/2 + 1):nrow(x), ])
samples_relabeled <- ord_ls(mcmc = fit[c(1:3)], d = 2, seed = 02222023)

# traceplots
mu_tbl <- tibble(
  trace = c(samples_relabeled$mu),
  param = rep(colnames(samples_relabeled$mu), each = nrow(samples_relabeled$mu)),
  iter = rep(1:nrow(samples_relabeled$mu), length(colnames(samples_relabeled$mu))),
  chain = 1,
  clus_id = stringr::str_sub(param, 4, 4), 
  dim = stringr::str_sub(param, 7, 7)
)
mu_tbl %>%
  filter(dim == 1) %>%
  ggplot(aes(x = iter, y = trace, col = clus_id)) +
  # facet_wrap(~ chain, labeller = label_both) +
  geom_line() +
  theme_bw() +
  labs(
    title = bquote("Traceplot for" ~ mu[1] * ", adjusted for label switching")
  )
mu_tbl %>%
  filter(dim == 2) %>%
  ggplot(aes(x = iter, y = trace, col = clus_id)) +
  # facet_wrap(~ chain, labeller = label_both) +
  geom_line() +
  theme_bw() +
  labs(
    title = bquote("Traceplot for" ~ mu[2] * ", adjusted for label switching")
  )

# plot lvs
z_mcmc <- samples_relabeled$other[,which(grepl("z", colnames(samples_relabeled$other)))]
z_tbl <- left_join(
  tibble(
    trace = c(z_mcmc),
    param = rep(colnames(z_mcmc), each = nrow(z_mcmc)),
    iter = rep(1:nrow(z_mcmc), length(colnames(z_mcmc))),
    obs_id = stringr::str_sub(
      param, 
      start = stringr::str_locate(param, pattern = "\\[")[,1] + 1,
      end = stringr::str_locate(param, pattern = "\\,")[,1] - 1
    ) %>% as.numeric(),
    dim = stringr::str_sub(
      param, 
      start = stringr::str_locate(param, pattern = "\\,")[,1] + 1,
      end = stringr::str_locate(param, pattern = "\\]")[,1] - 1
    ) %>% as.numeric()
  ),
  tibble(
    clus_id = c(samples_relabeled$clus_id),
    iter = rep(1:nrow(samples_relabeled$clus_id), length(colnames(samples_relabeled$clus_id))),
    obs_id = rep(1:ncol(samples_relabeled$clus_id), each = nrow(samples_relabeled$clus_id))
  ),
  by = c("iter", "obs_id")
)

@@

```{r}
rm(list = ls())
source("simulations/helpers.R")
source("coral.R")
```

## Simulation parameters

We will compare DPORD with the methods discussed in Hui et al (2017) when the number of clusters in the latent space is unknown. In total, these methods include:

- DPORD
- CORAL with DICc
- RPD with AICc
- Ward clustering, maximizing average silhouette width
- PAM with Bray-Curtis
- K-means, maximizing Calinkski-Harabasz index
- K-means, maximizing simple structure indices

For all methods but DPORD, candidate clusters from K = 2 to 10 will be considered. We will generate 100 data sets using COMPAS, considering 2, 3, 4, and 5 clusters in the latent space.

### COMPAS parameters

COMPAS requires coordinates of true site ordinations on a grid between 0 and 100, and specification of various mean abundances and sources of variation.

```{r, fig.dim = c(8, 10)}
compas_params <- list(
  k2 = list(
    mu = rbind(c(30, 60), c(60, 40)),
    sigma = rep(40, 2)
  ),
  k3 = list(
    mu = rbind(c(30, 30), c(70, 40), c(50, 70)),
    sigma = rep(40, 3)
  ),
  k4 = list(
    mu = rbind(c(30, 30), c(30,70), c(70,70), c(70,30)),
    sigma = rep(40, 4)
  ),
  k5 = list(
    mu = rbind(c(20, 20), c(20,80), c(80,80), c(80,20), c(50, 50)),
    sigma = rep(40, 5)
  )
)

# plot
plot_grid <- expand.grid(x = seq(0, 100, length.out = 100), y = seq(0, 100, length.out = 100))
plot_true_and_realizations(plot_grid, compas_params, ndx = 1)
plot_true_and_realizations(plot_grid, compas_params, ndx = 2)
plot_true_and_realizations(plot_grid, compas_params, ndx = 3)
plot_true_and_realizations(plot_grid, compas_params, ndx = 4)
```

```{r, eval = F}
set.seed(02232023)
compas_data <- list()

# k2
compas_data[[1]] <- lapply(
  1:100,
  function(x){
    set.seed(x);
    coords_ = rbind(
      mvtnorm::rmvnorm(15, compas_params$k2$mu[1,], compas_params$k2$sigma[1]*diag(2)),
      mvtnorm::rmvnorm(15, compas_params$k2$mu[2,], compas_params$k2$sigma[2]*diag(2))
    );
    list(
      true_coords = coords_, 
      Y =     compas(
        S = 50, 
        dims = 2,
        am = c(5, 5),
        beta.R = c(1, 1), 
        coords = coords_, 
        n.quanti = 1,
        n.quali = 0.05, 
        add1 = 0.05
      )
    )

  }
)

# k3
compas_data[[2]] <- lapply(
  1:100,
  function(x){
    set.seed(x);
    coords_ <- rbind(
        mvtnorm::rmvnorm(15, compas_params$k3$mu[1,], compas_params$k3$sigma[1]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k3$mu[2,], compas_params$k3$sigma[2]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k3$mu[3,], compas_params$k3$sigma[3]*diag(2))
      );
    list(
      true_coords = coords_, 
      Y =     compas(
        S = 50, 
        dims = 2,
        am = c(5, 5),
        beta.R = c(1, 1), 
        coords = coords_, 
        n.quanti = 1,
        n.quali = 0.05, 
        add1 = 0.05
      )
    )
  }
)

# k4
compas_data[[3]] <- lapply(
  1:100,
  function(x){
    set.seed(x);
    coords_ <- rbind(
        mvtnorm::rmvnorm(15, compas_params$k4$mu[1,], compas_params$k4$sigma[1]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k4$mu[2,], compas_params$k4$sigma[2]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k4$mu[3,], compas_params$k4$sigma[3]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k4$mu[4,], compas_params$k4$sigma[4]*diag(2))
      );
    list(
      true_coords = coords_, 
      Y =     compas(
        S = 50, 
        dims = 2,
        am = c(5, 5),
        beta.R = c(1, 1), 
        coords = coords_, 
        n.quanti = 1,
        n.quali = 0.05, 
        add1 = 0.05
      )
    )
  }
)

# k5
compas_data[[4]] <- lapply(
  1:100,
  function(x){
    set.seed(x);
    coords_ <- rbind(
        mvtnorm::rmvnorm(15, compas_params$k5$mu[1,], compas_params$k5$sigma[1]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[2,], compas_params$k5$sigma[2]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[3,], compas_params$k5$sigma[3]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[4,], compas_params$k5$sigma[4]*diag(2)),
        mvtnorm::rmvnorm(15, compas_params$k5$mu[5,], compas_params$k5$sigma[5]*diag(2))
      )
    list(
      true_coords = coords_, 
      Y =     compas(
        S = 50, 
        dims = 2,
        am = c(5, 5),
        beta.R = c(1, 1), 
        coords = coords_, 
        n.quanti = 1,
        n.quali = 0.05, 
        add1 = 0.05
      )
    )
  }
)
saveRDS(compas_data, file = "simulations/compas_data.rds")
```

```{r}
compas_data <- readRDS("simulations/compas_data.rds")
```
